---
title: "Star Wars Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cerulean
    
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(dplyr)
library(plotly)
library(wordcloud2)
library(hash)
source("helpers.R")
```

```{r data}

scripts = read.csv('CSV Files/scripts.csv')
tsne = read.csv('CSV Files/tsne.csv')
word_counts = read.csv('CSV Files/word_counts_by_movie.csv')
all_characters = unique(scripts %>% group_by(character) %>% summarize(n = n()) %>% arrange(desc(n)) %>% select(character))$character
all_films = c("EpisodeIV", "EpisodeV", "EpisodeVI")
# palette = colorRampPalette(c("#081d58", "#253494", "#225ea8", "#1d91c0", "#41b6c4", "#7fcdbb", "#c7e9b4", "#edf8b1", "#ffffd9"))
palette = colorRampPalette(c("#000000","#260101","#4D0303","#730505","#990606","#C00707","#E60909", "#EA290C","#EE490E","#F36911","#F78914","#FBA916","#FFC919", "#FFD23D","#FFDB62","#FFE486","#FFEDAA","#FFF6CF","#FFFFF3"))
# color_vec = c("022A99","2C4D83","56716D","819557","ABB840","D5DC2A","FFFF14")
# colors = c()
# for (color in color_vec){colors = c(colors, paste("#", color, sep = ""))}
# palette = colorRampPalette(colors)

```


TSNE Plot
=======================================================================



Column {.sidebar data-width=200}
-------------------------------------------------------------------
```{r}
selectInput(inputId = "characters_tsne", label = "Select Character(s):", choices = all_characters, multiple = TRUE, selected = all_characters)
selectInput(inputId = "films_tsne", label = "Select Film(s):", choices = all_films, multiple = TRUE, selected = all_films)
```


Column {}
-----------------------------------------------------------------------

### TSNE Plot

This plot is a 2D visual representation of a character's lines. The actual coordinates don't hold meaning, but the distance between points does. So, two points that are close together represent two characters with similar dialogue in the films.
The points in the graph are sized according to the number of lines, and colored according to average sentiment such that negative sentiment is colored red, and positive sentiment is yellow/white.


```{r}
renderPlotly({
  tsne_plot(input$characters_tsne, input$films_tsne, tsne, color_palette = palette)
})
```


Sentiment Analysis I
=======================================================================




Column {.sidebar data-width=200}
-------------------------------------------------------------------
```{r}
selectInput(inputId = "characters_sentiment", label = "Select Character(s):", choices = all_characters, multiple = TRUE, selected = c("LUKE", "VADER"))
selectInput(inputId = "films_sentiment", label = "Select Film(s):", choices = all_films, multiple = TRUE, selected = all_films)
```


Column {data-width=800}
-----------------------------------------------------------------------

### Sentiment over Time

This plot shows the sentiment score of a characters lines as the film exhibited evolves, as well as the approximated line of best fit through these lines. 


```{r}
renderPlotly({
  sentiment_time(input$characters_sentiment, input$films_sentiment, scripts, color_palette = palette)
})
```




Sentiment Analysis II
=======================================================================




Column {.sidebar data-width=200}
-------------------------------------------------------------------
```{r}
selectInput(inputId = "characters_sentiment2", label = "Select Character(s):", choices = all_characters, multiple = TRUE, selected = c("LUKE", "LEIA", "HAN", "VADER"))
selectInput(inputId = "films_sentiment2", label = "Select Film(s):", choices = all_films, multiple = TRUE, selected = all_films)
selectInput(inputId = "met_sentiment2", label = "Select Metric to Display:", choices = c("Sentiment", "Positive", "Neutral", "Negative"), selected = "Sentiment")
```


The metric to display corresponds to the type of sentiment that we analyze each character's lines on. "Sentiment" is the average general sentiment of a character's lines, "Positive" represents how positive a character's lines are on average, etc. 

Column {data-width=800}
-----------------------------------------------------------------------

### Sentiment over Line Count

This plot shows the average chosen sentiment metric over the total number of lines. The vertical axis represents how strongly the characters exhibit the chosen metric, and the horizontal axis shows the number of lines that character spoke. 


```{r}
renderPlotly({
  sentiment_over_lines(input$characters_sentiment, input$films_sentiment, scripts, met = input$met_sentiment2, color_palette = palette)
})
```


### Sentiment Bar Chart

This plot shows the average chosen sentiment metric of a character in each film selected in the sidebar.

```{r}
renderPlotly({
  sentiment_bar(input$characters_sentiment, input$films_sentiment, scripts, met = input$met_sentiment2, color_palette = palette)
})
```